The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-10-01 paper2_JNLS/paper.tex
NM
NNM

Our particular focus is the laboratory experiments of Bolles et al.~\cite{bolles2019anomalous}, who demonstrated the emergence of anomalous statistics in a randomized wave-field upon encountering an abrupt depth change (ADC). In these experiments, an incoming wave-field is generated with nearly Gaussian statistics, and a plexiglass step placed near the middle of the tank creates the depth change. Upon passing into the region of shallower depth, the wave distribution skews strongly, with deviation from Gaussian being most pronounced a short distance downstream of the ADC. 
Inspired by these experimental observations, Majda et al.~\cite{majda2019statistical} laid out a theoretical foundation that accurately captures several aspects of the anomalous behavior. The theory is based on deterministic and statistical analysis of the truncated Korteweg–de Vries (TKdV) equations, and uses a combination of computational, statistical, and analytical tools. In follow-up work, Majda and Qi (cite) performed analysis on more severely truncated, lower-dimensional systems that were shown to exhibit many of the same anomalous features.

@@

	As discussed in \cite{bolles2019anomalous}, the experiments consist of a long, narrow wave tank (6 m long x 20 cm wide x 30 cm high), with waves generated by plexiglass paddle at one end. The waves propagate through the tank and, roughly midway through, pass over an abrupt depth change (ADC), which is created by a plexiglass step. The waves continue to propagate through the shallower depth until reaching the far end of the tank, at which point their energy is dissipated by a horse-hair dampener. Since the dampener minimizes the backscatter, the waves in this experiment propagate primarily in one direction, from left to right in Fig.~\ref{fig1}.

@@

Figure \ref{uhist} shows histograms of the displacement $u$ from experiments and from TKdV theory. The experimental measurements have been normalized for comparison purposes. The comparison is fucking amazing!

@@

We show individual trajectories in the next figure for upstream and downstream. In the upstream flow, due to the coefficients, the nonlinearity is very weak. Hence, wave propagation is dominated by linear dispersion. Indeed, with weak nonlinearity, \eqref{dimlessKdV} is approximated by
\begin{equation}
u_t + C_2 \drat^{1/2} \, u_{xxx} = 0
\qquad \text{for } x \in [-\pi,\pi] \\
\end{equation}
which implies the dispersion relation $\omega_k = -C_2 k^3$ or for phase velocity $c_k = -C_2 k^2$, which implies left-going waves \cite{majdaqi2019}.

>>>>

Our particular focus is the laboratory experiments of Bolles et al.~\cite{bolles2019anomalous}, who demonstrated the emergence of anomalous statistics in a randomized wave-field upon encountering an abrupt depth change (ADC). In these experiments, an incoming wave-field is generated with nearly Gaussian statistics, and a plexiglass step placed near the middle of the tank creates the depth change. Upon passing into the region of shallower depth, the wave distribution skews markedly, with deviation from Gaussian being most pronounced a short distance downstream of the ADC. 
Inspired by these experimental observations, Majda et al.~\cite{majda2019statistical} laid out a theoretical foundation that accurately captures several aspects of the anomalous behavior. The theory is based on deterministic and statistical analysis of the truncated Korteweg–de Vries (TKdV) equations, and uses a combination of computational, statistical, and analytical tools. In follow-up work, Majda and Qi \cite{majdaqi2019} analyzed more severely truncated, lower-dimensional systems that were shown to exhibit many of the same anomalous features.

@@

	As discussed in \cite{bolles2019anomalous}, the experiments consist of a long, narrow wave tank (6 m long x 20 cm wide x 30 cm high), with waves generated by plexiglass paddle at one end. The waves propagate through the tank and, roughly midway through, pass over an abrupt depth change (ADC) created by a plexiglass step. The waves continue to propagate through the shallower depth until reaching the far end of the tank, at which point their energy is dissipated by a horse-hair dampener. Since the dampener minimizes the backscatter, the waves in this experiment propagate primarily in one direction, from left to right in Fig.~\ref{fig1}.

@@

Figure \ref{uhist} shows histograms of the displacement $u$ from experiments and from TKdV theory. The experimental measurements have been normalized for comparison purposes. The comparison is fucking amazing! Offers convincing evidence that the theory works and the parameters have been matched as well as possible. (At some point, I need to mention the minor point about the forcing spectrum not being matched to the Gibbs measure because it came first).

@@

We show individual trajectories in the next figure for upstream and downstream. In the upstream flow, due to the coefficients, the nonlinearity is very weak. Hence, wave propagation is dominated by linear dispersion. Indeed, with weak nonlinearity, \eqref{dimlessKdV} is approximated by
\begin{equation}
u_t + C_2 \drat^{1/2} \, u_{xxx} = 0
\qquad \text{for } x \in [-\pi,\pi] \\
\end{equation}
which implies the dispersion relation $\omega_k = -C_2 k^3$ or for phase velocity $c_k = -C_2 k^2$, which implies left-going waves \cite{majdaqi2019}.
% Further details, see page 6 of Majda Qi, J Stat Phys.

% Figure
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[!ht]
\begin{center}
\includegraphics[width = 0.99 \linewidth]{Figs/trajectories.pdf}
\caption{
Trajectories
}
\label{trajectories}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

% Figure
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[!ht]
\begin{center}
\includegraphics[width = 0.99 \linewidth]{Figs/skew-kurt.pdf}
\caption{
Skewness and kurtosis in DNS}
\label{skew-kurt}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
